H2 Supplement

### 2023-07-31 H2.Rmd
ran extra semi-clean analyses
added list of countries for age correlations

@@

@@

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
To interpret this we conducted a series of bivariate correlations to test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).

@@

@@

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
Again, to interpret this, we conducted a series of correlations to test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

>>>>

rownames(subset(test, p < .05))

@@

neg <- sum(test1$r <0 )
pos <- sum(test1$r>0)
neg

noquote(paste0(rownames(test1[which(test1$r<0),]),sep=", "))
noquote(paste0(rownames(test1[which(test1$r>0),]),sep=", "))

neg_names <- rownames(test1[which(test1$r<0),])
neg_names_first <- c(paste0(neg_names[1:(length(neg_names)-1)], sep = ", "))
neg_names_end <- c("and " , neg_names[length(neg_names)])
noquote(c(neg_names_first, neg_names_end))

pos_names <- rownames(test1[which(test1$r>0),])
pos_names_first <- c(paste0(pos_names[1:(length(pos_names)-1)], sep = ", "))
pos_names_end <- c("and " , pos_names[length(pos_names)])
noquote(c(pos_names_first, pos_names_end))

test1$r>0

@@

We conducted a linear-mixed-effects model to test if this relationship between age and internalization holds when participants are nested within country. Our outcome measure was internalization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
To interpret this we conducted a series of bivariate correlations to test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries. The countries with a positive correlation were `r noquote(paste0(c(pos_names_first, pos_names_end), collapse = ""))`, and the countries with a negative correlation were `r noquote(paste0(c(neg_names_first, neg_names_end), collapse = ""))`  (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Internalization)).

@@

neg_names <- rownames(test1[which(test1$r<0),])
neg_names_first <- c(paste0(neg_names[1:(length(neg_names)-1)], sep = ", "))
neg_names_end <- c("and " , neg_names[length(neg_names)])
noquote(c(neg_names_first, neg_names_end))

pos_names <- rownames(test1[which(test1$r>0),])
pos_names_first <- c(paste0(pos_names[1:(length(pos_names)-1)], sep = ", "))
pos_names_end <- c("and " , pos_names[length(pos_names)])
print(noquote(c(pos_names_first, pos_names_end)))
toString(noquote(paste0(c(pos_names_first, pos_names_end), collapse = "")))
help("toString")

toString(paste0(pos_names_first,collapse = ""))

noquote(paste0(c(pos_names_first, pos_names_end), collapse = ""))
noquote(paste0(c(neg_names_first, neg_names_end), collapse = ""))

@@

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and symbolization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
Again, to interpret this, we conducted a series of correlations to test if age was related to symbolization across all countries.  There was a significant correlation between age and symbolization in `r total_sig` countries. Of these, there was a positive correlation between age and symbolization in `r pos` countries, and a negative correlation in `r neg` countries. The countries with a positive correlation were `r noquote(paste0(c(pos_names_first, pos_names_end), collapse = ""))`, and the countries with a negative correlation were `r noquote(paste0(c(neg_names_first, neg_names_end), collapse = ""))` (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-07-31 H2_semi_clean.Rmd
ran extra semi-clean analyses
added list of countries for age correlations

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and internalization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
Again, to interpret this, we conducted a series of correlations to test if age was related to internalization across all countries.  There was a significant correlation between age and internalization in `r total_sig` countries. Of these, there was a positive correlation between age and internalization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

>>>>

Similarly, for symbolization, we conducted a linear-mixed-effects model to test if the relationship between age and symbolization holds when participants are nested within country. Our outcome measure was symbolization and our predictor variable was age; we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`, *p* `r paste(p_report(p1))`. 
There was a significant main effect for age,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between age and symbolization scores, $b$ = `r sprintf("%.3f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`,
*p* `r paste(p_report(p2))`.
Again, to interpret this, we conducted a series of correlations to test if age was related to symbolization across all countries.  There was a significant correlation between age and symbolization in `r total_sig` countries. Of these, there was a positive correlation between age and symbolization in `r pos` countries, and a negative correlation in `r neg` countries (see Supplementary Materials [Table S_X](https://cillianmiltown.github.io/moral_ID_gender/drafting_supplementary_analysis.html#Age__Symbolization)).

### 2023-07-31 H3.Rmd
added list of countries for age correlations

@@

>>>>

results_for_table$term <- c(
  "Intercept"
  ,"Power Distance"
  ,"Individualism"
  ,"Masculinity"
  ,"Uncertainty Avoidance"
  # ,"Long Term Orientation"
  # ,"Indulgence"
  # ,"Tightness: Domain General"
  # ,"Tightness: Domain Specific"
  # ,"Tightness: Combination Measure"
)

@@

# fit <- lm(moral_identity_symbolic ~
#                      age
#                     + sex3
#                     #+ age
#                     * (Power.Distance
#                     + Individualism
#                     + Masculinity
#                     + Uncertainty.Avoidance
#                     + Long.Term.Orientation
#                     + Indulgence
#                     + CTL_DG
#                     + CTL_DS
#                     + CTL_C)
#                 , data = x
#             )

### 2023-07-31 supp_H2.Rmd
added list of countries for age correlations

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")

@@

@@

@@

>>>>

#source("set_up_data_calculate_means.R")
load("data/data_with_means.RData")
#load("data/data_with_means_semi_clean.RData")

@@

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind
             , ps_output_for_table
             #, ps_for_table
             )
    )

@@

test1 <- subset(test, p < .05)
test1
test2 <- subset(test1, r < 0)

test2

@@

test[which(test$p<.05),]
